Title Goes Here

### 2023-09-26 paper/main.tex
wip
wrap up old laptop
sketch evaluation

\ExplSyntaxOn  %% for e.g. macro

\newcommand { \eg }  %% https://tex.stackexchange.com/a/639374/244649
{ \textit{e.g.}
  \peek_meaning_ignore_spaces:NTF .
    { \skip_horizontal:n { -.3ex } \use_none:n }
    { \peek_meaning_ignore_spaces:NF , { \skip_horizontal:n { -.3ex } } }
}
\newcommand { \ie }
{ \textit{i.e.}
  \peek_meaning_ignore_spaces:NTF .
    { \skip_horizontal:n { -.3ex } \use_none:n }
    { \peek_meaning_ignore_spaces:NF , { \skip_horizontal:n { -.3ex } } }
}

@@

>>>>

\ExplSyntaxOn    %% https://tex.stackexchange.com/a/639374/244649
\newcommand { \eg }
{ \textit{e.g.}
  \peek_meaning_ignore_spaces:NTF .
    { \skip_horizontal:n { -.3ex } \use_none:n }
    { \peek_meaning_ignore_spaces:NF , { \skip_horizontal:n { -.3ex } } }
}
\newcommand { \ie }
{ \textit{i.e.}
  \peek_meaning_ignore_spaces:NTF .
    { \skip_horizontal:n { -.3ex } \use_none:n }
    { \peek_meaning_ignore_spaces:NF , { \skip_horizontal:n { -.3ex } } }
}
\ExplSyntaxOff

@@

\section{Evaluation}

\subsection{Secure Protocols Evaluated}

\begin{table}
\centering
  \begin{tabular}{|l | l|l|}
    \hline
    \textbf{Protocol} & \textbf{Purpose} & \textbf{Ref.} \\
    \hline
    $n$-bit Addition & Custom & TODO \\
    Oblivious Transfer & Building block & TODO \\
    OT Extension & Building block & TODO \\
    Beaver Triple Generation & Building block & TODO \\
    GMW & Circuit evaluation & TODO \\
    MPC w/ Beaver Triples & Circuit evaluation & TODO \\
    \hline
  \end{tabular}
  \caption{Secure protocols used in our evaluation.}
\end{table}

\begin{table}
\centering
  \begin{tabular}{|l |l|l|}
    \hline
    \textbf{Circuit} & \textbf{AND Gates} & \textbf{Total Gates} \\
    \hline
    64-bit adder & 63 & 376 \\
    64-bit multiplier & 4,033 & 13,675 \\
    AES-128 & 6,400 & 36,663 \\
    SHA-256 & 22,573 & 135,073 \\
    Floating-point division & 82,269 & 184,007 \\
    \hline
  \end{tabular}
  \caption{Circuits used in our evaluation.}
\end{table}

\subsection{Experiment 1: Scalability for Secure Protocols}

\subsection{Experiment 2: Bug-Finding for Insecure Protocol Mutations}

\subsection{Experiment 3: Scalability and Bug-Finding for Random Programs}
